Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-04 paper/main.tex
add quantile chart
clarify number of input automata

We have used the tool \texttt{genltl} from Spot to generate LTL formulas
from literature and from scalable patterns. Using the values from 1 to 5 for
the parametrized formulas, we have generated 407 unique LTL formulas. These
have been translated to deterministic or nondeterministic TELA using four
state-of-the-art translators \texttt{ltl2tgba} (from the Spot library),
\texttt{ltl3tela}, \texttt{ltl2dela} (known as Delag), and \texttt{ltl2dgra}
(known as Rabinizer 4). The generated automata sets contain less than 407
automata as not all of the formulas are successfully translated due to timeouts.
Table \ref{tab:ltltranslators} shows the exact versions, the homepage of the
used tools and the number of input automata produced by the given tool from
the LTL formulas.

@@

\begin{table}[h]
\caption{LTL to automata translators used for the experimental evaluation
and the number of successfully translated formulas.}
\label{tab:ltltranslators}
\centering
\begin{tabular}{lr@{~~~}lr}
\toprule
tool        & version&homepage & \# formulas \\
\midrule
\texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 404\\
\texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} \todo{RELEASE} & 376\\
\texttt{ltl2dela} & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 397\\
\texttt{ltl2dgra} & 21.0 & & 386\\
\bottomrule
\end{tabular}
\end{table}

@@

%\begin{tikzpicture}
%\begin{axis}[
%	ymode=log,
%	height=5cm,
%	width=10cm,
%	grid=major,
%]
%\addplot coordinates {
%	(1, 0.3)
%	(2, 0.8)
%	(3, 1.5)
%	(4, 2.7)
%	(5, 3.9)
%	(6, 4.1)
%};
%\addlegendentry{Delag}
%\end{axis}
%\end{tikzpicture}

>>>>

We have used the tool \texttt{genltl} from Spot to generate LTL formulas
from literature and from scalable patterns. Using the values from 1 to 5 for
the parametrized formulas, we have generated 407 unique LTL formulas. These
have been translated to deterministic or nondeterministic TELA using four
state-of-the-art translators \texttt{ltl2tgba} (from the Spot library),
\texttt{ltl3tela}, \texttt{ltl2dela} (known as Delag), and \texttt{ltl2dgra}
(known as Rabinizer 4). The generated automata sets contain less than 407
automata as not all of the formulas are successfully translated due to timeouts.
We have also removed automata with 0 or 1 acceptance marks as there is little
point reducing these.
Table \ref{tab:ltltranslators} shows the exact versions, the homepage of the
used tools and the number of automata produced by the given tool from
the LTL formulas after filtering.

@@

\begin{table}[h]
\caption{LTL to automata translators used for the experimental evaluation
and the number of successfully translated formulas.}
\label{tab:ltltranslators}
\centering
\begin{tabular}{lr@{~~~}lr}
\toprule
tool        & version&homepage & automata \\
\midrule
\texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 89\\
\texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} \todo{RELEASE} & 108\\
\texttt{ltl2dela} & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 162\\
\texttt{ltl2dgra} & 21.0 & & 274\\
\bottomrule
\end{tabular}
\end{table}

@@

Looking at Figure~\ref{fig:quantile}, we ascertain that for every set, the
reduction of most automata takes under a second.

\begin{figure}[h]
\caption{Performance of \telatko on different automata sets. The $x$ axis
represents the number of reduced automata, the $y$ axis shows the time spent
reducing (in seconds).}
\label{fig:quantile}
\centering
\input{quantile.tex}
\end{figure}
